---
title: "Meta-analyses_example_090920"
author: "E. Bendall"
date: "09/09/2020"
output: word_document
---

```{r setup, include=TRUE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width=8, fig.height=6)


library(tidyverse)
library(ggplot2)
library(brms)
library(rstan)
library(here)
library(cli)
library(devtools)
library(revtools)
library(dmetar)
library(tidybayes)
library(readxl)
#devtools::install_github("MathiasHarrer/dmetar")

#These options help Stan run faster:

rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores())

# Make sure the scales package is available (it should be if ggplot is installed)
requireNamespace("scales")

# Default graph theme - white background
theme_set( theme_bw() )

set.seed(42)


# Set to TRUE to force models to be refitted
REFIT_MODELS <- FALSE


# Create a folder for fitted models if one does not already exist
FittedModelsPath <- here("fitted_models")
if (!dir.exists(FittedModelsPath)) {
  dir.create(FittedModelsPath)
}


# Load brms if it is installed (requires Stan software and the rstan package).
# If not installed, HAS_BRMS will be set to FALSE.
HAS_BRMS <- suppressWarnings(
  require("brms", quietly = TRUE)
)


###### Some helper functions #####

# Calculate standard page sizes
pagesize <- function(size = c("A4", "A3", "A2", "A1", "A0"), 
                     orientation = c("portrait", "landscape"),
                     units = c("cm", "mm")) {
  
  size <- match.arg(size)
  orientation <- match.arg(orientation)
  units <- match.arg(units)
  
  alpha <- 1000 * 2^(1/4)
  i <- as.integer(substr(size, 2, 2))
  long <- alpha * 2^(-i/2)
  
  page <- switch(
    orientation,
    portrait = c(width = long / sqrt(2), height = long),
    landscape = c(width = long, height = long / sqrt(2))
  )
  
  page <- round(page)
  if (units == "cm") page <- page / 10
  
  page <- c(as.list(page), units = units)
  class(page) <- "pagesize"
  
  page
}



# Save a graph to a PDF file
gg_pdf <- function(plot, filename, size = pagesize("A4", "landscape", "cm")) {
  
  if (!inherits(size, "pagesize")) stop("The size argument should be a pagesize (list) object")
  
  ggsave(
    filename, 
    plot, 
    width = size$width,
    height = size$height,
    units = size$units)
}


# Calculate highest posterior density interval for a vector of values
hpdi.vec <- function (x, prob = 0.95) {
  n <- length(x)
  if (n <= 1) stop("x must have more than 1 element")
  x <- sort(x)

  gap <- max(1, min(n - 1, round(n * prob)))
  init <- 1:(n - gap)

  inds <- which.min(x[init + gap] - x[init])

  out <- c(lower = x[inds], upper = x[inds + gap])
  out
}


```

```{r}
## load in files

data.bib <- read_bibliography(c("savedrecs (4).bib", "savedrecs (5).bib", "savedrecs (6).bib", "savedrecs (7).bib", "savedrecs (8).bib", "savedrecs (9).bib", "savedrecs (10).bib", "savedrecs (11).bib"))


# merge files

data <- merge_columns(data.bib, data.ris)
```


```{r}#
# locate duplicates
matches <- find_duplicates(data, match_variable = "title")
```

```{r}
# screen duplicate
result <- screen_duplicates(data.bib)

```

The screening identified 15 title matches, which were removed in the app

EXAMPLE: For the purposes of this example, we use dummy data

```{r}
ExcelPathData <- here("exampledata_quan.xlsx")

DAT.quan <- read_excel(ExcelPathData, guess_max = 26) %>%
  select(
         effective50,
         faunatype,
         actiontype,
         study,
         weights)
```

```{r}
DAT.quan <- DAT.quan %>%
  mutate(eff50 = ifelse(effective50 > 50, "effective", "not effective")) %>%
  mutate(actiontype = as.factor(actiontype)) %>%
  mutate(faunatype = as.factor(faunatype)) %>%
  mutate(study = as.factor(study))
```


```{r}#
# set priors
priors <- c(prior(normal(0,1), class = Intercept),
            prior(cauchy(0,0.5), class = sd))
```

## will need to figure out a way to calculate effects sizes. Will reporting and comparibility of this vary with study type?

```{r}#
# model 

library(future)

plan(multiprocess)

m.brm <- brm(eff50|weights(weights) ~ faunatype * actiontype + (1|study),
             data = DAT.quan,
             family = bernoulli(),
             warmup = 2000,
             iter = 30000,
             control = list(adapt_delta = 0.99,
                            max_treedepth = 18))

plan(sequential)

save(m.brm, file = "m.brm.Rdata")

load("m.brm.Rdata")
```

```{r}
load("m.brm.Rdata")
```




Model summary (similar to that from lme4::glmer). We only use this as a sanity check - not directly for inference.

```{r}
summary(m.brm)
```

These values are very similar to those produced by lme4::glmer.


Graphical summaries of fitted parameters (densities and trace plots). Again these are mostly for model checking.

```{r}

plot(m.brm)

```

```{r}
pp_check(m.brm)
```

```{r}
# summary of group level effects
ranef(m.brm)
```

```{r}
### create all unique combinations of variables (use expand.grid when cont. vars.)
post.m.brm <- expand.grid(
  faunatype = levels(DAT.quan$faunatype),
  actiontype = levels(DAT.quan$actiontype)) %>%
  
### add fitted draws  
  tidybayes::add_fitted_draws(m.brm, n = 3000, re_formula = NA) %>%
  ungroup() %>%
  
  mutate(actiontype = factor(actiontype, levels = c("1",   "2"),
                                         labels = c("one", "two"))) %>%

  select(iter = .draw, faunatype, actiontype, Probability = .value)

```

```{r}

effect <- post.m.brm %>%

tidyr::unite(actiontype_faunatype, actiontype, faunatype) %>%
  

  
  tidyr::spread(actiontype_faunatype, Probability)
  
```

```{r}
diffs <- effect %>%
  mutate(diff_A1_B = one_bird,
         diff_A1_M = one_mammal,
         diff_A2_B = two_bird,
         diff_A2_M = two_mammal) %>%
  
  select(starts_with("diff"))

head(diffs)

```



```{r}
diffs.1 <- effect %>%
  
  mutate(diff_mammal = (one_mammal -  two_mammal),
         diff_bird = (one_bird - two_bird)) %>%
  
  select(starts_with("diff"))

```

```{r}
# convert to long format for ggplot
dat.gg <- diffs %>%
  tidyr::gather(var, diff) %>%
  mutate(var = factor(str_replace(var, "diff_", ""))) %>%
  mutate(var = factor(str_replace(var, "_", "/"))) %>%
  mutate(var = factor(var, levels = c("A1/B", "A2/B", "A1/M", "A2/M"), 
                           labels = c("A1/B", "A2/B", "A1/M", "A2/M")))

## barktype, was problem with jagged lines  
x.stats <- dat.gg %>%
  group_by(var) %>%
    summarize(mid = median(diff),
                  lwr95 = hpdi.vec(diff, 0.95)[1],
                  upr95 = hpdi.vec(diff, 0.95)[2],
                  lwr50 = hpdi.vec(diff, 0.50)[1],
                  upr50 = hpdi.vec(diff, 0.50)[2])
```

```{r fig.height = 3, fig.width = 3}
#### main plot for effect1

library(ggthemes)
library(ggpubr)
library(egg)

rhg_cols2 <- c("grey15", "grey30", "grey53", "grey")
xtext <- c("no scar", "scar", "no scar", "scar", "no scar", "scar", "no scar", "scar")
ytext <- c("Pole-sized")
lines <- c("solid", "dashed", "dotted", "longdash")
My_Theme = theme(
  plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
  axis.title.y = element_text(size = 12, face = "bold"),
  axis.text.y = element_text(size = 10, margin = unit(c(0.1, 0.1, 0.1, -0.2), "cm")),
  axis.text.x = element_text(size = 11, vjust = 0, margin = unit(c(0.15, 0.1, 0.1, 0.1), "cm")),
  axis.title.x = element_text(size = 12, face = "bold", vjust = -1.8),
  strip.text.x = element_text(size = 11),
  strip.text.y = element_text(size = 11),
  strip.text = element_text(size = 11),
  strip.background = element_blank(),
  panel.background = element_blank(),
  strip.placement = "inside",
  axis.ticks.length = unit(-0.07, "cm"),
  axis.ticks = element_line(size = 0.8),
  panel.grid.minor.x = element_blank(),
  panel.grid.major.x = element_blank(),
  panel.grid.minor.y = element_blank(),
  panel.grid.major.y = element_blank(),
  legend.position = c(0.150, 0.70),
  legend.title = element_text(size = 9, hjust = 0.6, face = "bold"),
  legend.text = element_text(size = 9),
  legend.key.width = unit(0.3, "cm"),
  legend.key.height = unit(0.5, "cm"),
  legend.background = element_blank(),
  plot.margin = unit(c(6, 6, 6, 6), "pt"))



example1 <- ggplot(data = dat.gg, aes(x = var)) +
  
   My_Theme +
  
  geom_linerange(data = x.stats, aes(ymin = lwr95, ymax = upr95),
               size = 0.5) +
 
   geom_linerange(data = x.stats, aes(ymin = lwr50, ymax = upr50),
               size = 3.5, show.legend = FALSE) +
  

  labs(y = "", x = "Action type / faunatype", title = "") +
  
  scale_color_brewer(palette = "Dark2") 
 
 
  annotate_figure(example1, left = text_grob("P effectiveness > 50 %", face = "bold", rot = 90, vjust = 0.9))
   
ggsave("example1.png")
```

